---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# BrBS

<!-- badges: start -->
<!-- badges: end -->

The goal of BrBS is to provide convenient functions for reading portions of the BBS database into R, performing exploratory analyses, and creating visualizations.

## Installation

You can install the development version of BrBS from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("BibelnieksDFW/BrBS")
```

## Usage

A typical workflow for exploring survey data begins by selecting an island to look at, and then reading in the corresponding sheet from the database. 

```{r Setup}
library(BrBS)
## Read in Saipan data, get years, etc...
```

Once we have the data for that island read in, we may want to look at survey conduct metrics over the years. 

```{r Survey Conduct}
## Observer, number of stations, start times, which birds can we look at....
```

To look at trends in counts over the years, we need to first identify the bird species we want to consider. Then we can plot basic trends over time.

```{r Trends}
## Basic plotting of counts...
```
